A Sample JFE Paper\footnotetext{Financial support from \ldots}

### 2018-03-16 Paper/Paper.tex

We estimate the two parameters using maximum likelihood estimation. Our theoretical model gives a probability mass distribution for every whole number of citations, but the actual data shows fractional values (this is due to the diffusive correction factor from Hall et al., 2001). To address this, we rounded the expected citation variable to the nearest whole number, and then took the likelihood as the theoretical PMF value at that point.

The resulting parameter estimates are shown in figure 6, and the fit is plotted in figure 7.  The estimated ratio of incremental to abrupt patents is about 10:1, which is consistent with the fact that we defined the upper ten percent of patents in the citation distribution as being abrupt. The estimate of $\alpha$ is equal to one. This indicates that firms do not face diminishing returns to initial investment. This has very important theoretical implications, which will be discussed later on.

\begin{table}[htbp] \centering \captionsetup{width=5.8in}
    \caption{\label{MLETable}\textit{Results from the maximum likelihood estimation}}
	\centering
	\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm} llp{1.5cm}}
	\toprule
	MLE & \multicolumn{1}{c}{$\alpha$} & \multicolumn{1}{c} {$\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$} \\ 
	\midrule
	Results & 10.06 & 7.39\\
	Mean of first 5 seq. ratios & 0.57 & 0.88\\
	Sum of first 2 bins & 0.26 & 0.22\\
	R\&D Intensity & 0.068 & 0.068\\
	Criterion & & 0.386\\
	\midrule
	$(\hat{\tau} + \hat{\lambda}_{int,abr}, \hat{\lambda}_{inc,0}, \hat{\alpha}) = (0.047, 0.351, 1)$\\
	\bottomrule
	\end{tabular}
\end{table}

Looking at figure 7, we see that the data fits most of the distribution closely (including the upper tail, which is not pictured), but significantly underestimates the amount of zero-citation patents. We find that, when observations in the upper tail are eliminated, the estimation better fits the zero-citation data (see figure 8), indicating that the model is unable to completely capture both of those features. Now, it may seem fairly ad-hoc to eliminate observations in the upper tail, but there may be a theoretical justification for doing so. Our model, in keeping with AK2016, only allows for two scales of innovation: abrupt and incremental. This assumption seems to be made only for mathematical simplicity; while there is plenty of evidence that some patents are more valuable than others, there seems to be no evidence of a binary distinction. One might expect that patents in the upper tail of our empirical distribution (it had a max of 741 citations) are significantly more productive than the others. However, under our simple binary model, those patents are identical to the others from a productivity standpoint, and the only reason they gained more citations was through chance. Thus, because a more complete model may place the upper-tail observations in a separate classification, it is reasonable to be suspicious of estimation results that are pinned down by the upper tail.

Multiple methods were used to make sure that the parameter values given in figure 6 were in fact those that maximize the log-likelihood function. First, many initial values were used in the optimization algorithm, and it always gave the same result. We also tried fixing the value of $\alpha$ and running an unconstrained optimization to determine $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$, and this also gave the same result (the motivation being that the unconstrained algorithm is sometimes less sensitive to initial conditions). Finally, the 3d plot of the negative log-likelihood clearly shows a minimum at our parameter values (see figure 8), and a basin hopping algorithm found no other minimum.

Recall that our empirical distribution likely underestimates the number of abrupt patents with a low number of citations. This implies that our theoretical model may actually be even worse at fitting the zero-citation density than figure 7 would suggest. It also implies that our estimate of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ may be biased downward. Importantly, however, because lowering $\alpha$ leads to a decrease in the theoretical density at zero, this downward bias is probably not impacting our estimate of $\alpha$; if the bias was corrected, we would still expect $\alpha$ to be equal to one.

\subsection{First Robustness Check: GMM Estimation}

Before drawing strong conclusions from our estimation, we ran several robustness checks. These were meant to test the sensitivity of our estimates both to changes in the estimation procedure and to changes in theoretical assumptions.  We are mainly interested in seeing if $\alpha$ remains equal to one (no diminishing returns to incremental innovations) and if the model's fit to the data is affected.

First, we re-estimated the parameters using an alternative estimation scheme: Generalized Method of Moments. The adopted strategy was to estimate $\hat{\theta}_{GMM} = (\tau + \lambda_{int,abr}, \lambda_{inc,0}, \alpha)$ by solving equation~\eqref{eq:GMM} with the actual and the estimated moments ($m^d(x)$ and $m^e(x|\theta_{GMM})$, respectively, where $x$ is the real data).

@@

As far as theoretical assumptions, one of our most arbitrary is the assumption that abrupt patents are those in the upper ten percent of the total citation distribution. While the ten percent value is similar to the one estimated by AK2016, and is used in other papers, those papers use a different theoretical model. Furthermore, there is no defining feature of the citation distribution at the ten percent cutoff (no discontinuity or anything). Considering this, it is necessary to check whether our results are robust to changes in this cutoff.

The MLE estimates for cutoffs of 20\% and 5\%, alongside the baseline results, are shown in figure 9. We see that the arrival rates move in the direction that you would expect; the relative amount of abrupt patents drops when the cutoff is 5\% and increases when the cutoff is 20\%. More importantly, we find that $\alpha$ is still equal to one.

Next we focused on the assumption that an incremental patent will always cite the abrupt patent that initiated its technology cluster. This assumption, which we initially made for mathematical simplicity, is inconsistent with the conclusions of AK2016. In their model, they included a certain probability $p$ that an abrupt patent will be cited by subsequent incremental patents, which was estimated to be 75\%. Adding this parameter to our model is simple. For a technology cluster of size $k$, the probability of the abrupt patent having $i$ citations is given by the binomial distribution:
\begin{equation} \label{eq:prob}
Prob_{i, k} = Binom{i, k, p}
\end{equation}
Thus, given the size distribution $\eta_k$ from equations 14-15, the citation distribution $f_i$ is given by:
\begin{equation} \label{eq:cit_dist}
f_i = \displaystyle\sum_{k=0}^{\infty}\eta_k * Prob_{i, k}
\end{equation}
The addition of the probability parameter $p$ gives the model more flexibility. A lower value of $p$ shifts the distribution left.

The MLE estimates for this updated model are presented in table 10 and figure 11. We see that $p$ is equal to one, with the other parameters identical to our baseline model. This seems to validate our original assumption of setting $p$ equal to one. There are a few caveats, however, with this robustness check. First, as was mentioned above, even in our baseline model there is a problem with the classification of abrupt patents. It is likely that abrupt patents which are displaced early on by another abrupt patent will never gain enough citations to reach our cutoff value. This leads our empirical distribution (shown in figure 2) to underestimate the number of abrupt patents with a low number of citations. When the probability of citing is less than one, we would expect this underestimation to be even greater. This bias could cause us to overestimate the value of $p$.

@@

>>>>

We estimate the two parameters using a Maximum Likelihood Estimation (MLE). Our theoretical model gives a probability mass distribution for every whole number of citations, but the actual data shows fractional values (this is due to the diffusive correction factor from Hall et al., 2001). To address this, we rounded the expected citation variable to the nearest whole number, and then took the likelihood as the theoretical PMF value at that point.

The resulting parameter estimates are shown in table \ref{tab:MLETable}, and the fit is plotted in figure \ref{fig:MLE}. The estimated ratio of incremental to abrupt patents is about 10:1, which is consistent with the fact that we defined the upper 10\% of patents in the citation distribution as being abrupt. The estimate of $\alpha$ is equal to one. This indicates that firms do not face diminishing returns to initial investment. This has very important theoretical implications, which will be discussed later on.

\begin{table}[htbp] \centering \captionsetup{width=5.8in}
    \caption{\label{tab:MLETable}\textit{Results from the maximum likelihood estimation}}
	\centering
	\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{0.5cm} p{0.5cm}}
	\toprule
	MLE & \multicolumn{1}{c}{$\alpha$} & \multicolumn{1}{c}{$\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$} & \multicolumn{1}{c}{Criterion}\\
	\midrule
	Results & 1.0 & 0.0995 & 634983.15\\
	\bottomrule
	\end{tabular}
\end{table}

Looking at figure \ref{fig:MLE}, we see that the data fits most of the distribution closely (including the upper-tail, which is not pictured), but significantly underestimates the amount of zero-citation patents. We find that, when observations in the upper tail are eliminated, the estimation better fits the zero-citation data (see figure \ref{fig:MLE_extail}), indicating that the model is unable to completely capture both of those features. Now, it may seem fairly ad-hoc to eliminate observations in the upper tail, but there may be a theoretical justification for doing so. Our model, in keeping with Akcigit and Kerr (2016), only allows for two scales of innovation: abrupt and incremental. This assumption, while it allows for some mathematical simplicity, is clearly a simplification of reality. While there is plenty of evidence that some patents are more valuable than others, there seems to be no evidence of a binary distinction. One might expect that patents in the upper tail of our empirical distribution (it had a max of 741 citations) are significantly more productive than the others. However, under our binary model, those patents are identical to the others from a productivity standpoint, and the only reason they gained more citations was through chance. Thus, because a more complete model may place the upper-tail observations in a separate classification, it is reasonable to be suspicious of estimation results that are pinned down by the upper-tail.

Multiple methods were used to make sure that the parameter values given in figure \ref{fig:MLE} were in fact those that maximize the log-likelihood function. First, many initial values were used in the optimization algorithm, and it always gave the same result. We also tried fixing the value of $\alpha$ and running an unconstrained optimization to determine $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$, and this also gave the same result (the motivation being that the unconstrained algorithm is sometimes less sensitive to initial conditions). Finally, the 3D plot of the negative log-likelihood clearly shows a minimum at our parameter values (see figure \ref{fig:Crit}), and a basin hopping algorithm found no other minimum.

Recall that our empirical distribution likely underestimates the number of abrupt patents with a low number of citations. This implies that our theoretical model may actually be even worse at fitting the zero-citation density than figure \ref{fig:MLE_extail} would suggest. It also implies that our estimate of $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$ may be biased downward. Importantly, however, because lowering $\alpha$ leads to a decrease in the theoretical density at zero, this downward bias is probably not impacting our estimate of $\alpha$; if the bias was corrected, we would still expect $\alpha$ to be equal to one.

\subsection{First Robustness Check: Generalized Method of Moments Estimation}

Before drawing strong conclusions from our estimation, we ran several robustness checks. These were meant to test the sensitivity of our estimates both to changes in the estimation procedure and to changes in theoretical assumptions. We are mainly interested in seeing if $\alpha$ remains equal to one (no diminishing returns to incremental innovations) and if the fit of the model to the data is affected.

First, we re-estimated the parameters using an alternative estimation scheme: Generalized Method of Moments (GMM). The adopted strategy was to estimate $\hat{\theta}_{GMM} = (\tau + \lambda_{int,abr}, \lambda_{inc,0}, \alpha)$ by solving equation~\eqref{eq:GMM} with the actual and the estimated moments ($m^d(x)$ and $m^e(x|\theta_{GMM})$, respectively, where $x$ is the real data).

@@

As far as theoretical assumptions, we will now test the robustness of our estimates to variations in the 10\% cutoff that defines an abrupt innovation. While the 10\% value is similar to the one estimated by Akcgit and Kerr (2016) and is used in other papers, those papers use a different theoretical model. Furthermore, there is no defining feature of the citation distribution at the 10\% cutoff (e.g. no discontinuity or anything). Considering this, it is necessary to check whether our results are robust to changes in this cutoff.

The MLE estimates for cutoffs of 20\% and 5\%, alongside the baseline results, are shown in table \ref{tab:Cutoff}. We see that the arrival rates move in the direction that you would expect; the relative amount of abrupt patents drops when the cutoff is 5\% and increases when the cutoff is 20\%. More importantly, we find that $\alpha$ is still equal to one.

\begin{table}
	\caption*{MLE results for different abrupt cutoff levels.}
	\centering\label{tab:Cutoff}
	\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm}}
		\toprule
		Abrupt Cutoff & \multicolumn{1}{c}{10\%} & \multicolumn{1}{c}{20\%} & \multicolumn{1}{c}{5\%}\\ 
		\midrule
		$\lambda_{inc, 0}$ & 0.357 & 0.362 & 0.347 \\
		$(\lambda_{abr} + \tau)$ & 0.0355 & 0.0239 & 0.0568\\
		$\alpha$ & 1.0 & 1.0 & 1.0\\
		\bottomrule
	\end{tabular}
\end{table}

Next we focused on the assumption that an incremental patent will always cite the abrupt patent that initiated its technology cluster. This assumption, which we initially made for mathematical simplicity, is inconsistent with the conclusions of Akcigit and Kerr (2016). In their model, they included a certain probability $p$ that an abrupt patent will be cited by subsequent incremental patents, which was estimated to be 75\%. Adding this parameter to our model is simple. For a technology cluster of size $k$, the probability of the abrupt patent having $i$ citations is given by the binomial distribution:

\begin{equation} \label{eq:prob}
Prob_{i, k} = Binom{i, k, p}
\end{equation}

Thus, given the size distribution $\eta_k$ from equations \ref{eq:eta0} and \ref{eq:etak}, the citation distribution $f_i$ is given by:

\begin{equation} \label{eq:cit_dist}
f_i = \displaystyle\sum_{k=0}^{\infty}\eta_k * Prob_{i, k}
\end{equation}

The addition of the probability parameter $p$ gives the model more flexibility. A lower value of $p$ shifts the distribution left.

The MLE estimates for this updated model are presented in table \ref{tab:Prob} and figure 11. We see that $p$ is equal to one, with the other parameters identical to our baseline model. This seems to validate our original assumption of setting $p$ equal to one. There are a few caveats, however, with this robustness check. First, as was mentioned above, even in our baseline model there is a problem with the classification of abrupt patents. It is likely that abrupt patents which are displaced early on by another abrupt patent will never gain enough citations to reach our cutoff value. This leads our empirical distribution (shown in figure 2) to underestimate the number of abrupt patents with a low number of citations. When the probability of citing is less than one, we would expect this underestimation to be even greater. This bias could cause us to overestimate the value of $p$.

\begin{table}
	\caption*{Robustness Specification Results}
	\centering\label{tab:Prob}
	\begin{tabular}{l llp{1.5cm} p{0.5cm} llp{1.5cm}}
		\toprule
		    & \multicolumn{1}{c}{Baseline} & \multicolumn{1}{c}{Flexible}\\ 
		\midrule
		$\frac{\lambda_{inc, 0}}{(\lambda_{abr} + \tau)}$ & .104 & .104 \\
		$\alpha$ & 1.0 & 1.0\\
		$p$ & - & 1.0 \\
		log-likelihood & -627597 & -627598 \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\begin{figure}[htb]\centering \captionsetup{width=5.8in}
    \fbox{\resizebox{3.0in}{2.0in}{\includegraphics{MLE.png}}}
    \caption{\label{fig:MLE}\textit{Maximum likelihood estimated curve plotted over the same-class citation distribution.}}
\end{figure}

\begin{figure}[htb]\centering \captionsetup{width=5.8in}
    \fbox{\resizebox{3.0in}{2.0in}{\includegraphics{MLE_extail.png}}}
    \caption{\label{fig:MLE_extail}\textit{Maximum likelihood estimated curves using the entire distribution or excluding the upper-tail.}}
\end{figure}

\begin{figure}[htb]\centering \captionsetup{width=5.8in}
    \fbox{\resizebox{3.0in}{2.0in}{\includegraphics{Crit.png}}}
    \caption{\label{fig:Crit}\textit{3D plot of the criterion function of the maximum likelihood estimation for values of $\alpha$ and $\frac{\lambda_{abr, int} + \tau}{\lambda_{inc,0}}$.}}
\end{figure}
